---
title: "Clustering Analysis"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

::: panel-tabset
```{r}

library(lme4)
library(kableExtra)
library(sjPlot)

load("clean_data/bns_combined.Rdata")


```

# Fast Food Clustering by Campus

```{r}


fit_partpool_ff <- lmer(ff_numeric ~ (1 |school), data=bns_combined)

sjPlot::plot_model(fit_partpool_ff, type="re", sort.est = "(Intercept)", y.offset = .4, vline.color = "black")

tab_model(fit_partpool_ff)

```

> The ICC is low for fast food intake. The amount of variance within group compared to across group is negligible

```{r}

showri_ff <- data.frame(Random_Effect   = unlist(ranef(fit_partpool_ff)), 
                     Fixed_Intercept = fixef(fit_partpool_ff), 
                     RandomIntercept = unlist(ranef(fit_partpool_ff))+fixef(fit_partpool_ff))
                
rownames(showri_ff) <- rownames(coef(fit_partpool_ff)$school)

kbl(showri_ff) %>%
  kable_paper("hover", full_width = F)

```

> There is lots of overlap of CIs between the schools. For fast-food consumption, there was significantly different random effects from Cal State LA and CSU Dominguez Hills

# SSB Clustering by Campus

```{r}


fit_partpool_ssb <- lmer(ssb_numeric ~ (1 |school), data=bns_combined)

sjPlot::plot_model(fit_partpool_ssb, type="re", sort.est = "(Intercept)", y.offset = .4,  vline.color = "black")

tab_model(fit_partpool_ssb)


```

> The ICC is low for SSB intake. The amount of variance within group compared to across group is negligible

```{r}

showri_ssb <- data.frame(Random_Effect   = unlist(ranef(fit_partpool_ssb)), 
                     Fixed_Intercept = fixef(fit_partpool_ssb), 
                     RandomIntercept = unlist(ranef(fit_partpool_ssb))+fixef(fit_partpool_ssb))
                
rownames(showri_ssb) <- rownames(coef(fit_partpool_ssb)$school)

kbl(showri_ssb) %>%
  kable_paper("hover", full_width = F)

```

> There is lots of overlap of CIs between the schools. For SSB intake, there were significantly different random effects for Butte, Cal State LA, UC BErkeley and Chico State.

# F&V Clustering by Campus

```{r}

bns_combined$fruits_numeric <- as.numeric(bns_combined$fruits3, na.rm = TRUE)

fit_partpool_fruits <- lmer(fruits_numeric ~ (1 |school), data=bns_combined)

sjPlot::plot_model(fit_partpool_fruits, type="re", sort.est = "(Intercept)", y.offset = .4, vline.color = "black")

tab_model(fit_partpool_fruits)

```

> The ICC is low for SSB intake. The amount of variance within group compared to across group is negligible

```{r}

showri_fruits <- data.frame(Random_Effect   = unlist(ranef(fit_partpool_fruits)), 
                     Fixed_Intercept = fixef(fit_partpool_fruits), 
                     RandomIntercept = unlist(ranef(fit_partpool_fruits))+fixef(fit_partpool_fruits))
                
rownames(showri_fruits) <- rownames(coef(fit_partpool_fruits)$school)

kbl(showri_fruits) %>%
  kable_paper("hover", full_width = F)

```

> There is lots of overlap of CIs between the schools.
:::
