---
title: "Manuscript Files"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

> This page shows all graphs and tables used in the manuscript along with the code used. Additional univariate frequencies of covariates not shown in the manuscript are shown in the demographics table.



```{r, include=FALSE}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(gtsummary)
library(performance)
library(mice)
library(kableExtra)
library(dotwhisker)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(tidymodels)


bns_imputed_mids <- readRDS("clean_data/imp_bns_combined_clean_mids.RData")

bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)

load("clean_data/bns_combined.Rdata")

chc.palette <- c("#B1D238", "#5782B0", "#FF914D")

bns_combined_imputed_df$calfresh3 <- recode(bns_combined_imputed_df$calfresh3, "CalFresh" = "CalFresh Recipients", "Likely Not Eligible" = "Income-Ineligible Non-Recipients",
"No CalFresh but Likely Eligible" = "Likely Eligible Non-Recipients")

bns_combined$calfresh3 <- recode(bns_combined$calfresh3, "CalFresh" = "CalFresh Recipients", "Likely Not Eligible" = "Income-Ineligible Non-Recipients",
"No CalFresh but Likely Eligible" = "Likely Eligible Non-Recipients")



```

# Frequency Statistics

## Table 1: Demographic Information:

```{r, echo=FALSE}
bns_combined$school2 <- recode(bns_combined$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

bns_combined_imputed_df$school2 <- recode(bns_combined_imputed_df$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

```

```{r}




demographics_cc <- bns_combined %>% select(age, gender, race_eth, monthly_hh_income, academic_level, Cohort, school2, calfresh3, calfresh_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)

cc <- demographics_cc %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


demographics_imp <- bns_combined_imputed_df %>% select(age, gender, race_eth, monthly_hh_income, academic_level, Cohort, school2, calfresh3, calfresh_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)



imp <- demographics_imp %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


tbl_merge(tbls = list(cc, imp), 
          tab_spanner = c("**Complete Case Demographics**", "**Imputed Demographics**")) %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```

## Figure 2: Fast Food Vs CalFresh

```{r}


bns_combined_imputed_df$ff_cat2 <- recode(bns_combined_imputed_df$ff_cat,
                                          "Zer" = "Zero",
                                          "1-2 times per week" = "1-2 times",
                                          "3-4 times per week" = "3-4 times",
                                          "5 or more times per week" = "5 or more times")

p2 <- bns_combined_imputed_df %>% select(ff_cat2, calfresh3) %>% na.omit() %>% ggplot(aes(x= ff_cat2,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
     geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.85))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nFrequency of Fast-Food Meals Per Week") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

# ggsave("FF_Plot.png", plot = p2, width = 10, height = 8)

p2

```

## Figure 3: SSB Vs CalFresh

```{r}

p3 <- bns_combined %>% select(ssb_cat, calfresh3) %>% na.omit() %>% ggplot(aes(x= ssb_cat,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) + 
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 1.6))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nOunces of Sugar Sweetened Beverages Consumed Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

# ggsave("SSB_Plot.png", plot = p3, width = 10, height = 8)

p3



```

## Figure 4: F&V Vs CalFresh

```{r}


p1 <- bns_combined_imputed_df %>% select(fruits3, calfresh3) %>% na.omit() %>% ggplot(aes(x= fruits3,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.6))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nServings of Fruits and Vegetables Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

  # ggsave("FV_Plot.png", plot = p1, width = 10, height = 8)

p1

```

# Ordinal Regression Models

## Table 2: Fast Food Ordinal

```{r}

ff.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ff_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()

ff.ordinal.mod


```

## Table 3: SSB Ordinal

```{r}



ssb.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ssb_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


ssb.ordinal.mod


```

## Table 4: F&V Ordinal

```{r}

FV.ordinal.mod <- with(bns_imputed_mids, MASS::polr(fruits3~calfresh3 + Cohort + gender + race_eth + age + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()



FV.ordinal.mod

```

# All Ordinal Models

```{r}

tbl_merge(tbls = list(ff.ordinal.mod, ssb.ordinal.mod, FV.ordinal.mod), tab_spanner = c("F&V Model", "**Fast Food Model**", "**SSB Model**"))

```
