---
title: "Manuscript Files"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

```{r, include=FALSE}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(gtsummary)
library(performance)
library(mice)
library(kableExtra)
library(dotwhisker)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(tidymodels)


bns_imputed_mids <- readRDS("clean_data/imp_bns_combined_clean_mids.RData")

bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)

load("clean_data/bns_combined.Rdata")

chc.palette <- c("#B1D238", "#5782B0", "#FF914D")

bns_combined_imputed_df$calfresh3 <- recode(bns_combined_imputed_df$calfresh3, "CalFresh" = "CalFresh Recipients", "Likely Not Eligible" = "Income-Ineligible Non-Recipients",
"No CalFresh but Likely Eligible" = "Likely Eligible Non-Recipients")

bns_combined$calfresh3 <- recode(bns_combined$calfresh3, "CalFresh" = "CalFresh Recipients", "Likely Not Eligible" = "Income-Ineligible Non-Recipients",
"No CalFresh but Likely Eligible" = "Likely Eligible Non-Recipients")



```

# Frequency Statistics

::: panel-tabset
## Demographic Information:

```{r, echo=FALSE}
bns_combined$school2 <- recode(bns_combined$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

bns_combined_imputed_df$school2 <- recode(bns_combined_imputed_df$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

```


```{r}




demographics_cc <- bns_combined %>% select(age, gender, race_eth, monthly_hh_income, academic_level, Cohort, school2, calfresh3, calfresh_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)

cc <- demographics_cc %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


demographics_imp <- bns_combined_imputed_df %>% select(age, gender, race_eth, monthly_hh_income, academic_level, Cohort, school2, calfresh3, calfresh_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)



imp <- demographics_imp %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


tbl_merge(tbls = list(cc, imp), 
          tab_spanner = c("**Complete Case Demographics**", "**Imputed Demographics**")) %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```

## Dependent variables Vs CalFresh Table

```{r}
bns_combined_imputed_df %>% select(ff_cat, ssb_cat, fruits3, calfresh3) %>% tbl_summary(by = calfresh3, missing = "no") %>% add_overall(last = TRUE) %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```

## FV Vs CalFresh Plot

```{r}


p1 <- bns_combined_imputed_df %>% select(fruits3, calfresh3) %>% na.omit() %>% ggplot(aes(x= fruits3,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.4))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nServings of Fruits and Vegetables Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

  # ggsave("FV_Plot.png", plot = p1, width = 10, height = 8)

p1

```

## Fast Food Vs CalFresh Plot

```{r}


bns_combined_imputed_df$ff_cat2 <- recode(bns_combined_imputed_df$ff_cat,
                                          "Zer" = "Zero",
                                          "1-2 times per week" = "1-2 times",
                                          "3-4 times per week" = "3-4 times",
                                          "5 or more times per week" = "5 or more times")

p2 <- bns_combined_imputed_df %>% select(ff_cat2, calfresh3) %>% na.omit() %>% ggplot(aes(x= ff_cat2,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
     geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.85))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nFrequency of Fast-Food Meals Per Week") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

# ggsave("FF_Plot.png", plot = p2, width = 10, height = 8)

p2

```

## SSB Vs CalFresh Plot

```{r}

p3 <- bns_combined %>% select(ssb_cat, calfresh3) %>% na.omit() %>% ggplot(aes(x= ssb_cat,  group=calfresh3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(calfresh3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) + 
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~calfresh3, ncol = 1, scales = "free_x") +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 1.6))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nOunces of Sugar Sweetened Beverages Consumed Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

# ggsave("SSB_Plot.png", plot = p3, width = 10, height = 8)

p3



```
:::

# SSB Intake

::: panel-tabset
## SSB Ordinal

```{r}



ssb.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ssb_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


ssb.ordinal.mod  %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )



```

## Stratified Logistic Reg

```{r}

ordinal.mod1 <-glm(ssb_cat1~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod2 <-glm(ssb_cat2~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod3 <-glm(ssb_cat3~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")


ordinal.mod1 <- tidy(ordinal.mod1) %>%
  mutate(model = "Model 1")

ordinal.mod2 <- tidy(ordinal.mod2) %>%
  mutate(model = "Model 2")

ordinal.mod3 <- tidy(ordinal.mod3) %>%
  mutate(model = "Model 3")

models <- bind_rows(ordinal.mod1, ordinal.mod2, ordinal.mod3)

dwplot(models)

```

## Compare AIC and BIC

```{r}

linear.model <- lm(ssb_numeric~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df)


poisson.model <- glm(ssb_numeric~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "poisson")

log.model <- glm(log(ssb_numeric + 0.01)~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df)

ordinal.mod <- MASS::polr(ff_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)


AIC(poisson.model)
AIC(linear.model)
AIC(log.model)
AIC(ordinal.mod)

BIC(poisson.model)
BIC(linear.model)
BIC(log.model)
BIC(ordinal.mod)


```

## Model Fit

```{r}


ssb.ordinal.mod2 <- MASS::polr(ssb_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)

preds_SSB <- augment(ssb.ordinal.mod2, type = "class")
conf_mat(preds_SSB, truth = ssb_cat, estimate = .fitted)
accuracy(preds_SSB, truth = ssb_cat, estimate = .fitted)



```

## VIF of a Linear Model

```{r}
linear.model <- lm(ssb_numeric~calfresh3 + Cohort + gender + race_eth + age + physical_activity + health_conscious + storage_access + units_four + paid_work_hours_tens + caregiving_hours_tens + homelessness_year, data = bns_combined_imputed_df)

car::vif(linear.model)


```
:::

# Fast Food Intake

::: panel-tabset
## Fast Food Ordinal

```{r}

ff.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ff_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()

ff.ordinal.mod %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )


```

## Stratified Logistic Reg

```{r}

ordinal.mod1 <-glm(ff_cat1~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod2 <-glm(ff_cat2~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod3 <-glm(ff_cat3~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, family = "binomial")


ordinal.mod1 <- tidy(ordinal.mod1) %>%
  mutate(model = "1-2 Vs Zero")

ordinal.mod2 <- tidy(ordinal.mod2) %>%
  mutate(model = "3-4 Vs 1-2")

ordinal.mod3 <- tidy(ordinal.mod3) %>%
  mutate(model = "5 or more Vs 3-4")

models <- bind_rows(ordinal.mod1, ordinal.mod2, ordinal.mod3)

dwplot(models)

```

## Compare AIC and BIC

```{r}

linear.model <- lm(ff_numeric~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df)


poisson.model <- glm(floor(ff_numeric)~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, family = "poisson")

log.model <- glm(log(ff_numeric + 0.01)~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df)

ordinal.mod <- MASS::polr(ff_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)


AIC(poisson.model)
AIC(linear.model)
AIC(log.model)
AIC(ordinal.mod)

BIC(poisson.model)
BIC(linear.model)
BIC(log.model)
BIC(ordinal.mod)


```

## Model Fit

```{r}
ff.ordinal.mod2 <- MASS::polr(ff_cat~calfresh3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + cooking_confident + food_insecure_2item + paid_work_hours_tens + living_with_family + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)

preds_ff <- augment(ff.ordinal.mod2, type = "class")
conf_mat(preds_ff, truth = ff_cat, estimate = .fitted)
accuracy(preds_ff, truth = ff_cat, estimate = .fitted)

```
:::

# FV Intake

::: panel-tabset
## FV Ordinal

```{r}

FV.ordinal.mod <- with(bns_imputed_mids, MASS::polr(fruits3~calfresh3 + Cohort + gender + race_eth + age + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()

FV.ordinal.mod %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```

## Stratified Logistic Reg

```{r}

imp_one_vs_zero <- with(bns_imputed_mids, glm(q77_one_vs_zero~calfresh3 + Cohort + gender + race_eth + age + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item, family = "binomial"))



imp_one_vs_three_or_more <- with(bns_imputed_mids, glm(q77_one_vs_three_or_more~calfresh3 + Cohort + gender + race_eth + age + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item, family = "binomial"))


```

```{r}

imp_fv1_model_tidy <- pool(imp_one_vs_zero) |> summary() %>%
  mutate(model = "Odds of Eating 1-2 F&V Vs Zero",
         estimate = exp(estimate)) %>% select(-df)


imp_fv2_model_tidy <- pool(imp_one_vs_three_or_more) |> summary() %>%
  mutate(model = "Odds of Eating 3 or More F&V Vs 1-2",
         estimate = exp(estimate)) %>% select(-df)


FV2_models <- bind_rows(imp_fv1_model_tidy, imp_fv2_model_tidy)


dwplot(FV2_models) + geom_vline(xintercept = 1,
               colour = "grey60",
               linetype = 2) +
    theme(legend.title = element_blank(),
          legend.position = c(0.8, 0.95), text = element_text(size = 10, face = "bold")) + xlab("Odds Ratio")

```

## Model Accuracy

```{r}

FV.ordinal.mod2 <- MASS::polr(fruits3~calfresh3 + Cohort + gender + race_eth + age + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item, data = bns_combined_imputed_df, Hess=TRUE)

preds_FV <- augment(FV.ordinal.mod2, type = "class")
conf_mat(preds_FV, truth = fruits3, estimate = .fitted)
accuracy(preds_FV, truth = fruits3, estimate = .fitted)

```
:::

# All Ordinal Models

```{r}

tbl_merge(tbls = list(FV.ordinal.mod, ff.ordinal.mod, ssb.ordinal.mod), tab_spanner = c("F&V Model", "**Fast Food Model**", "**SSB Model**")) %>%
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```
