---
title: "Manuscript Files"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

> This page shows all graphs and tables used in the manuscript along with the code used. Additional univariate frequencies of covariates not shown in the manuscript are shown in the demographics table.

```{r, include=FALSE}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(gtsummary)
library(performance)
library(mice)
library(kableExtra)
library(dotwhisker)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(tidymodels)


bns_imputed_mids <- readRDS(here::here("clean_data/imp_bns_combined_clean_mids.RData"))

bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)

load("clean_data/bns_combined.Rdata")

chc.palette <- c("#B1D238", "#5782B0", "#FF914D")




# Set figure labels
figure_labels <- c("SNAP Recipient" = "SNAP Recipients (n = 670)", 
              "Income-Ineligible Non-Recipient" = "Income-Ineligible Non-Recipients (n = 321)", 
              "Likely Eligible Non-Recipient" = "Likely Eligible Non-Recipients (n = 1,371)")




```

# Frequency Statistics

## Table 1: Demographic Information:

```{r, echo=FALSE}
bns_combined$school2 <- recode(bns_combined$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

bns_combined_imputed_df$school2 <- recode(bns_combined_imputed_df$school,
                             "Allan Hancock Community College" = "CC",
                             "Butte CC" = "CC", "Mt. SAC CC" = "CC", "Clovis CC" = "CC",
                             "Palo Verde CC" = "CC", 
                             "Cal State San Bernardino" = "CSU",
                             "CSU Bakersfield" = "CSU",
                             "Fresno State" = "CSU",
                             "Sacramento State" = "CSU",
                             "Chico State" = "CSU",
                             "CSU Dominguez Hills" = "CSU",
                             "San Francisco State" = "CSU",
                             "Cal State LA" = "CSU",
                             "CSU, Northridge" = "CSU",
                             "UC Berkeley" = "UC")

```

```{r}




demographics_cc <- bns_combined %>% select(age, gender, race_eth, academic_level, Cohort, school2, SNAP3, SNAP_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)

cc <- demographics_cc %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


demographics_imp <- bns_combined_imputed_df %>% select(age, gender, race_eth, academic_level, Cohort, school2, SNAP3, SNAP_eligible, cooking_confident, health_conscious, physical_activity, ssb_cat, ff_cat, fruits3, food_insecure_2item,  units, paid_work_hours)



imp <- demographics_imp %>% 
  tbl_summary(statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


tbl_merge(tbls = list(cc, imp), 
          tab_spanner = c("**Non-imputed Demographics**", "**Imputed Demographics**")) %>% 
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
    )

```

## Figure 2: Fast Food Vs SNAP

```{r}


bns_combined_imputed_df$ff_cat2 <- recode(bns_combined_imputed_df$ff_cat,
                                          "Zero" = "Zero",
                                          "1-2 times per week" = "1-2 times",
                                          "3-4 times per week" = "3-4 times",
                                          "5 or more times per week" = "5 or more times")

p2 <- bns_combined_imputed_df %>% select(ff_cat2, SNAP3) %>% na.omit() %>% ggplot(aes(x= ff_cat2,  group=SNAP3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(SNAP3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
     geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~SNAP3, ncol = 1, scales = "free_x",
               labeller = as_labeller(figure_labels)) +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.85))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nFrequency of Fast-Food Meals Per Week") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

# ggsave("FF_Plot.png", plot = p2, width = 8, height = 6)

p2

```

## Figure 3: SSB Vs SNAP

```{r}



p3 <- bns_combined_imputed_df %>% select(ssb_cat, SNAP3) %>% na.omit() %>% ggplot(aes(x= ssb_cat,  group=SNAP3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(SNAP3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) + 
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~SNAP3, ncol = 1, scales = "free_x",
               labeller = as_labeller(figure_labels)) +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 1.6))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nOunces of Sugar Sweetened Beverages Consumed Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

 # ggsave("SSB_Plot.png", plot = p3, width = 8, height = 6)

p3



```

## Figure 4: F&V Vs SNAP

```{r}

p1 <- bns_combined_imputed_df %>% select(fruits3, SNAP3) %>% na.omit() %>% ggplot(aes(x= fruits3,  group=SNAP3)) + 
    geom_bar(aes(y = ..prop.., fill = factor(SNAP3)), stat="count",
             #alpha = c(0.3, 0.7, 1, 0.3, 0.7, 1, 0.3, 0.7, 1), 
             colour="black", size=0.6) +
    geom_text(aes(label = scales::percent(round(..prop.., digits = 2)), y=..prop..), stat= "count", vjust = -.5, size = 6) +
    labs(y = "Percent of Students") +
    facet_wrap(~SNAP3, ncol = 1, scales = "free_x", 
               labeller = as_labeller(figure_labels)) +
    scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0.0, 0.6))) +
  scale_fill_manual(values = chc.palette) +
  theme_bw() + theme(legend.position="none") + 
  xlab("\nServings of Fruits and Vegetables Per Day") + theme(strip.text.x = element_text(size = 15), text = element_text(size = 15))

  # ggsave("FV_Plot.png", plot = p1, width = 8, height = 6)

p1

```

# Table 2

```{r}



bns_combined_imputed_df %>% select(SNAP3, fruits3, ssb_cat, ff_cat) %>%
  tbl_summary(by = SNAP3, statistic = list(
      all_continuous() ~ "Mean: {mean}, Median: {median}, SD: {sd}",
      all_categorical() ~ "{n} ({p}%)"),
      missing_text= "Missing (n)")


```

# Ordinal Regression Models

## Table 2: Fast Food Ordinal

```{r}

ff.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()

ff.ordinal.mod


```

## Table 3: SSB Ordinal

```{r}



ssb.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


ssb.ordinal.mod


```

## Table 4: F&V Ordinal

```{r}

FV.ordinal.mod <- with(bns_imputed_mids, MASS::polr(fruits3~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()



FV.ordinal.mod

```

# All Ordinal Models

```{r}

tbl_merge(tbls = list(ff.ordinal.mod, ssb.ordinal.mod, FV.ordinal.mod), tab_spanner = c("**Fast Food Model**", "**SSB Model**", "**F&V Model**"))

```

