---
title: "Model Diagnostics"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

> This page shows all procedures used to choose the best fitting model. The BIC and AIC of a Poisson, linear, log transformation, and an ordinal regression model were compared. The ordinal regression models fit the best and had the lowest AICs and BICs. To ensure that there were no major differences in results across the different levels of the dependent variables, stratified logistic regressions were fitted and compared. All results appeared to stay consistent across the different levels, justifying the use of an ordinal regression model.

```{r, include=FALSE}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(mice)
library(dplyr)
library(tidymodels)
library(dotwhisker)

bns_imputed_mids <- readRDS("clean_data/imp_bns_combined_clean_mids.RData")



bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)


```

::: panel-tabset
# Fast Food Model Diagnostic

## Stratified Logistic Regressions

```{r}

ordinal.mod1 <-glm(ff_cat1~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod2 <-glm(ff_cat2~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod3 <-glm(ff_cat3~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "binomial")


ordinal.mod1 <- tidy(ordinal.mod1) %>%
  mutate(model = "1-2 Vs Zero",
         estimate = exp(estimate))

ordinal.mod2 <- tidy(ordinal.mod2) %>%
  mutate(model = "3-4 Vs 1-2",
         estimate = exp(estimate))

ordinal.mod3 <- tidy(ordinal.mod3) %>%
  mutate(model = "5 or more Vs 3-4",
         estimate = exp(estimate))

models <- bind_rows(ordinal.mod1, ordinal.mod2, ordinal.mod3)

dwplot(models) + geom_vline(xintercept = 1,
               colour = "grey60",
               linetype = 2) +
                xlab("Odds Ratio")

```

> In almost all variables, confidence intervals overlapped between stratified models and estimates were similar, meaning there were no major differences between levels and an ordinal regression is appropriate. 

## Compare AIC and BIC

```{r}

linear.model <- lm(ff_numeric~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df)


poisson.model <- glm(floor(ff_numeric)~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, family = "poisson")

log.model <- glm(log(ff_numeric + 0.01)~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df)

ordinal.mod <- MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)

cat("AIC for Poisson Model:", AIC(poisson.model))

cat("AIC for Linear Model:", AIC(linear.model))

cat("AIC for Log Transformation Model:", AIC(log.model))

cat("AIC for Ordinal Model:", AIC(ordinal.mod))


cat("BIC for Poisson Model:", BIC(poisson.model))

cat("BIC for Linear Model:", BIC(linear.model))

cat("BIC for Log Transformation Model:", BIC(log.model))

cat("BIC for Ordinal Model:", BIC(ordinal.mod))


```

> Although AIC and BIC are computed differently between model types, the ordinal model had far lower values, justifying the use of an ordinal regression

## Model Accuracy

```{r}
ff.ordinal.mod2 <- MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)

preds_ff <- augment(ff.ordinal.mod2, type = "class")
conf_mat(preds_ff, truth = ff_cat, estimate = .fitted)
accuracy(preds_ff, truth = ff_cat, estimate = .fitted)

```

> This model had 56% accuracy

## Colinearity

```{r}

# Check VIF of a linear model
linear.model <- lm(ff_numeric~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df)

car::vif(linear.model)

```

> There were no variables that were highly colinear.

# SSB Model Diagnostics

## Stratified Logistic Reg

```{r}

ordinal.mod1 <-glm(ssb_cat1~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod2 <-glm(ssb_cat2~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, family = "binomial")

ordinal.mod3 <-glm(ssb_cat3~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, family = "binomial")


ordinal.mod1 <- tidy(ordinal.mod1) %>%
  mutate(model = "1-8 ounces Vs Zero",
          estimate = exp(estimate))

ordinal.mod2 <- tidy(ordinal.mod2) %>%
  mutate(model = "9-16 ounces Vs 1-8",
          estimate = exp(estimate))

ordinal.mod3 <- tidy(ordinal.mod3) %>%
  mutate(model = "17 or more ounces Vs 9-16",
          estimate = exp(estimate))

models <- bind_rows(ordinal.mod1, ordinal.mod2, ordinal.mod3)

dwplot(models) + geom_vline(xintercept = 1,
               colour = "grey60",
               linetype = 2) +
                xlab("Odds Ratio")

```

> In almost all variables, confidence intervals overlapped between stratified models and estimates were similar, meaning there were no major differences between levels and an ordinal regression is appropriate. 

## Compare AIC and BIC

```{r}

linear.model <- lm(ssb_numeric~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df)


poisson.model <- glm(ssb_numeric~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, family = "poisson")

log.model <- glm(log(ssb_numeric + 0.01)~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df)

ordinal.mod <- MASS::polr(ff_cat~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)


cat("AIC for Poisson Model:", AIC(poisson.model))

cat("AIC for Linear Model:", AIC(linear.model))

cat("AIC for Log Transformation Model:", AIC(log.model))

cat("AIC for Ordinal Model:", AIC(ordinal.mod))


cat("BIC for Poisson Model:", BIC(poisson.model))

cat("BIC for Linear Model:", BIC(linear.model))

cat("BIC for Log Transformation Model:", BIC(log.model))

cat("BIC for Ordinal Model:", BIC(ordinal.mod))



```

> Although AIC and BIC are computed differently between model types, the ordinal model had far lower values, justifying the use of an ordinal regression

## Model Accuracy

```{r}


ssb.ordinal.mod2 <- MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df, Hess=TRUE)

preds_SSB <- augment(ssb.ordinal.mod2, type = "class")
conf_mat(preds_SSB, truth = ssb_cat, estimate = .fitted)
accuracy(preds_SSB, truth = ssb_cat, estimate = .fitted)



```

> The SSB model had 42% accuracy

## Colinearity

```{r}

# Check VIF of a linear model
linear.model <- lm(ssb_numeric~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, data = bns_combined_imputed_df)

car::vif(linear.model)


```

> There were no variables that were highly colinear.

# F&V Model Diagnostics

## Stratified Logistic Regressions

```{r}

imp_one_vs_zero <- with(bns_imputed_mids, glm(q77_one_vs_zero~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, family = "binomial"))



imp_one_vs_three_or_more <- with(bns_imputed_mids, glm(q77_one_vs_three_or_more~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, family = "binomial"))


imp_fv1_model_tidy <- pool(imp_one_vs_zero) |> summary() %>%
  mutate(model = "1-2 F&V Vs Zero",
         estimate = exp(estimate)) %>% select(-df)


imp_fv2_model_tidy <- pool(imp_one_vs_three_or_more) |> summary() %>%
  mutate(model = "3 or More F&V Vs 1-2",
         estimate = exp(estimate)) %>% select(-df)


FV2_models <- bind_rows(imp_fv1_model_tidy, imp_fv2_model_tidy)


dwplot(FV2_models) + geom_vline(xintercept = 1,
               colour = "grey60",
               linetype = 2) +
                xlab("Odds Ratio")

```

> In almost all variables, confidence intervals overlapped between stratified models and estimates were similar, meaning there were no major differences between levels and an ordinal regression is appropriate. 


## Compare AIC and BIC

```{r}

linear.model <- lm(q77_numeric~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df)


poisson.model <- glm(floor(q77_numeric)~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df, family = "poisson")

log.model <- glm(log(q77_numeric + 0.01)~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df)

ordinal.mod <- MASS::polr(fruits3~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df, Hess=TRUE)

cat("AIC for Poisson Model:", AIC(poisson.model))

cat("AIC for Linear Model:", AIC(linear.model))

cat("AIC for Log Transformation Model:", AIC(log.model))

cat("AIC for Ordinal Model:", AIC(ordinal.mod))


cat("BIC for Poisson Model:", BIC(poisson.model))

cat("BIC for Linear Model:", BIC(linear.model))

cat("BIC for Log Transformation Model:", BIC(log.model))

cat("BIC for Ordinal Model:", BIC(ordinal.mod))

```

> Although AIC and BIC are computed differently between model types, the ordinal model had far lower values, justifying the use of an ordinal regression

## Model Accuracy

```{r}

FV.ordinal.mod2 <- MASS::polr(fruits3~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df, Hess=TRUE)

preds_FV <- augment(FV.ordinal.mod2, type = "class")
conf_mat(preds_FV, truth = fruits3, estimate = .fitted)
accuracy(preds_FV, truth = fruits3, estimate = .fitted)

```

> This model had a 72% accuracy

## Colinearity

```{r}

# Check VIF of a linear model
linear.model <- lm(q77_numeric~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df)

car::vif(linear.model)

```

> There were no variables that were highly colinear.

:::
