---
title: "Statewide vs Pilot 2 Cohort Comparison"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---


```{r, include=FALSE}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(gtsummary)
library(performance)
library(mice)
library(kableExtra)
library(dotwhisker)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(tidymodels)


bns_imputed_mids <- readRDS(here::here("clean_data/imp_bns_combined_clean_mids.RData"))

bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)

load("clean_data/bns_combined.Rdata")

chc.palette <- c("#B1D238", "#5782B0", "#FF914D") 
```




> This page shows the comparison between the ordinal models of the statewide cohort and the second pilot cohort when analyzed separately. An additional model was also compared including only CSU juniors and seniors from the statewide cohort (to more closely match the second pilot cohort). Overall, the statewide and second pilot study displayed similar results as seen with the considerable overlap between the confidence intervals in all comparisons, however there were some differences between a few variables. Wide confidence intervals were seen in the second pilot study which can be explained by uncertainty from the lower sample size. The decision was made to include both cohorts in the analysis for the manuscript and to control for differences between cohorts.

> When analyzing the second pilot study and statewide data separately, the second pilot study’s results tended to have wider confidence intervals compared to the statewide study with considerable overlap between the cohorts for all variables in each model. However, some differences in the results between the cohorts were present, where most of the differences were due to the uncertainty from the lower sample size. Other differences can be explained by the timeframe of the second pilot study, from 2020 – 2021, which was collected during the COVID-19 stay-at-home orders, and many students were living with their families, attending colleges virtually. 

> It should be noted that when analyzing the second pilot study separately, there were no significant associations between SNAP and all three diet indicators after controlling for covariates. Similar findings were seen when filtering the statewide data to only include juniors and seniors from CSU campuses (to more closely match the second pilot’s cohort). In both cases, these results can also be attributed to the uncertainty in the data from the lower sample sizes as seen with the wide confidence intervals, especially when comparing IINRs to SNAP recipients, where the number of IINRs was rather low. 

> Another important difference between the cohorts was that the effect of physical activity on F&V intake in the statewide data was stronger than in the second pilot study. This difference could be due to the COVID-19 lockdown causing disruptions in students’ diet and physical activity routines, leading to students shifting to at home workouts and living with their families.  


```{r}
bns_imputed_mids_sw <- bns_imputed_mids %>% filter(Cohort == "Statewide")


bns_imputed_mids_sw2 <- bns_imputed_mids %>% filter(Cohort == "Statewide",
                                                   school2 == "CSU",
                                                   academic_level == "Junior" | academic_level == "Senior")



bns_imputed_mids_p2 <- bns_imputed_mids %>% filter(Cohort == "Pilot 2")


```


## Fast Food Ordinal



```{r}

ff.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE))

ff.ordinal.mod.p2 <- with(bns_imputed_mids_p2, MASS::polr(ff_cat~SNAP3 + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE))

ff.ordinal.mod.sw <- with(bns_imputed_mids_sw, MASS::polr(ff_cat~SNAP3 + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE))

ff.ordinal.mod.sw2 <- with(bns_imputed_mids_sw2, MASS::polr(ff_cat~SNAP3 + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE))


```



```{r, fig.height=7}

ff.ordinal.mod.tidy <- pool(ff.ordinal.mod) |> summary() %>%
  mutate(model = "Combined Model")
  

ff.ordinal.mod.p2.tidy <- pool(ff.ordinal.mod.p2) |> summary() %>%
  mutate(model = "Pilot 2 Only") %>% select(-df)

ff.ordinal.mod.sw.tidy <- pool(ff.ordinal.mod.sw) |> summary() %>%
  mutate(model = "Statewide Only") %>% select(-df)

ff.ordinal.mod.sw2.tidy <- pool(ff.ordinal.mod.sw2) |> summary() %>%
  mutate(model = "Statewide CSU/Juniors and Seniors") %>% select(-df)


ff_models <- bind_rows(ff.ordinal.mod.p2.tidy, ff.ordinal.mod.sw.tidy, ff.ordinal.mod.sw2.tidy, ff.ordinal.mod.tidy)


# Drop slopes from plot
ff_models <- ff_models[-c(17:19, 36:38, 55:57, 75:77), ]

dwplot(ff_models) + geom_vline(xintercept = 0,
               colour = "black",
               linetype = 1) + xlab("Beta and CI") + 
  theme(legend.position='top')  + guides(colour = guide_legend(nrow = 2, title = ""))






```







## SSB Ordinal

```{r}

ssb.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE)) 

ssb.ordinal.mod.p2 <- with(bns_imputed_mids_p2, MASS::polr(ssb_cat~SNAP3 + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE))  

ssb.ordinal.mod.sw <- with(bns_imputed_mids_sw, MASS::polr(ssb_cat~SNAP3 + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE))


ssb.ordinal.mod.sw2 <- with(bns_imputed_mids_sw2, MASS::polr(ssb_cat~SNAP3 + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE))




```


```{r, fig.height=7}


ssb.ordinal.mod.tidy <- pool(ssb.ordinal.mod) |> summary() %>%
  mutate(model = "Combined Model")

ssb.ordinal.mod.p2.tidy <- pool(ssb.ordinal.mod.p2) |> summary() %>%
  mutate(model = "Pilot 2 Only") %>% select(-df)

ssb.ordinal.mod.sw.tidy <- pool(ssb.ordinal.mod.sw) |> summary() %>%
  mutate(model = "Statewide Only") %>% select(-df)

ssb.ordinal.mod.sw2.tidy <- pool(ssb.ordinal.mod.sw2) |> summary() %>%
  mutate(model = "Statewide CSU/Juniors and Seniors") %>% select(-df)


ssb_models <- bind_rows(ssb.ordinal.mod.p2.tidy, ssb.ordinal.mod.sw.tidy, ssb.ordinal.mod.sw2.tidy,ssb.ordinal.mod.tidy)

# Drop slopes from plot
ssb_models <- ssb_models[-c(17:19, 36:38, 55:57, 75:77), ]

dwplot(ssb_models) + geom_vline(xintercept = 0,
               colour = "black",
               linetype = 1) + xlab("Beta and CI") + 
  theme(legend.position='top') + guides(colour = guide_legend(nrow = 2, title = ""))


```






## F&V Ordinal

```{r}

FV.ordinal.mod <- with(bns_imputed_mids, MASS::polr(fruits3~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE))

FV.ordinal.mod.p2 <- with(bns_imputed_mids_p2, MASS::polr(fruits3~SNAP3 + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE))

FV.ordinal.mod.sw <- with(bns_imputed_mids_sw, MASS::polr(fruits3~SNAP3 + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE))

FV.ordinal.mod.sw2 <- with(bns_imputed_mids_sw2, MASS::polr(fruits3~SNAP3 + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE))




```




```{r, fig.height=7}

FV.ordinal.mod.tidy <- pool(FV.ordinal.mod) |> summary() %>%
  mutate(model = "Combined Model")

FV.ordinal.mod.p2.tidy <- pool(FV.ordinal.mod.p2) |> summary() %>%
  mutate(model = "Pilot 2 Only") %>% select(-df)

FV.ordinal.mod.sw.tidy <- pool(FV.ordinal.mod.sw) |> summary() %>%
  mutate(model = "Statewide Only") %>% select(-df)

FV.ordinal.mod.sw2.tidy <- pool(FV.ordinal.mod.sw2) |> summary() %>%
  mutate(model = "Statewide CSU/Juniors and Seniors") %>% select(-df)


FV_models <- bind_rows(FV.ordinal.mod.p2.tidy, FV.ordinal.mod.sw.tidy, FV.ordinal.mod.sw2.tidy, FV.ordinal.mod.tidy)


# Drop slopes from plot
FV_models <- FV_models[-c(15:16, 31:32, 47:48, 64:65), ]


dwplot(FV_models, est.type = "odds") + geom_vline(xintercept = 0,
               colour = "black",
               linetype = 1) + xlab("Beta and CI")  + 
  theme(legend.position='top') + guides(colour = guide_legend(nrow = 2, title = ""))




```













