---
title: "Variable Selection"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

> This page shows all steps taken for variable selection. Potentially relevant variables from the survey were identified based on a theoretical approach and previous qualitative studies among college students. A LASSO regression was first used to identify which variables are relevant to each model. A ten-fold cross validation was used to determine the minimum lambda value (the optimum level of regularization). General linear regression models were then fit for each dependent variable including all potential covariates using the optimum level of regularization. Academic level was not included as a potential covariate since the pilot 2 cohort included no freshmen and sophomores.

> Age, gender, and race/ethnicity were included as covariates in all models regardless of the LASSO regression results due to previous literature indicating associations with diet outcomes. Cohort was also included in all models to control for differences between the two cohorts. Covariates with high p-values were then removed from the models if removing them had no major impact on the results, to help prevent overfitting the models.

::: panel-tabset
```{r}
knitr::opts_chunk$set(error = FALSE,warning = FALSE,message = FALSE,echo = TRUE)

library(nnet)
library(glmnet)
library(gglasso)
library(mice)
library(gtsummary)
library(car)


bns_imputed_mids <- readRDS(here::here("clean_data/imp_bns_combined_clean_mids.RData"))

bns_combined_imputed_df <- complete(bns_imputed_mids, fill = 3)


```

# Fast Food LASSO Regression

```{r}


y <- bns_combined_imputed_df$ff_numeric
x <- model.matrix(ff_numeric~SNAP3 + Cohort + race_eth + gender + age + cooking_confident + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + kitchen_access + storage_access + storage_room  + physical_activity + firstgen + household_size  + housing_insecure + homelessness_year, bns_combined_imputed_df)[,-1] # the -1 drops the intercept
model.lasso <- glmnet(x, y, alpha = 1)


set.seed(123) # Setting a seed to ensure I get the same results each time I knit
cv.lasso <- cv.glmnet(x, y, alpha = 1)

# Fit the final model using the min lambda
model <- glmnet(x, y, alpha = 1, lambda = cv.lasso$lambda.min)

round(coef(model), digits = 1)

```

> 0.1 appeared to be a reasonable cutoff. Based on this cutoff, covariates will include homelessness, physical activity, storage room, kitchen access, health consciousness, paid work hours, food insecurity, living with family, cooking confidence, gender, race/eth, and Cohort. Gender, age, race/eth, and cohort were included in all models regardless of LASSO results

# SSB LASSO Regression

```{r}


y <- bns_combined_imputed_df$ssb_numeric
x <- model.matrix(ssb_numeric~SNAP3 + Cohort + race_eth + gender + age + cooking_confident + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + kitchen_access + storage_access + storage_room  + physical_activity + firstgen + household_size  + housing_insecure + homelessness_year, bns_combined_imputed_df)[,-1] # the -1 drops the intercept
model.lasso <- glmnet(x, y, alpha = 1)


set.seed(123) # Setting a seed to ensure I get the same results each time I knit
cv.lasso <- cv.glmnet(x, y, alpha = 1)

# Fit the final model using the min lambda
model <- glmnet(x, y, alpha = 1, lambda = cv.lasso$lambda.min)

round(coef(model), digits = 1)

```

> Using a cutoff of 0.1, all variables except for kitchen access and cooking confident may contribute to the model

# F&V LASSO Regression

```{r}

y <- bns_combined_imputed_df$q77_numeric
x <- model.matrix(q77_numeric~SNAP3 + Cohort + race_eth + gender + age + cooking_confident + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + kitchen_access + storage_access + storage_room  + physical_activity + firstgen + household_size  + housing_insecure + homelessness_year, bns_combined_imputed_df)[,-1] # the -1 drops the intercept
model.lasso <- glmnet(x, y, alpha = 1)


set.seed(123) # Setting a seed to ensure I get the same results each time I knit
cv.lasso <- cv.glmnet(x, y, alpha = 1)

# Fit the final model using the min lambda
model <- glmnet(x, y, alpha = 1, lambda = cv.lasso$lambda.min)

round(coef(model), digits = 1)

```

> Using a cutoff of 0.1, covariates will include first generation, physical activity, storage room, health consciousness, food insecurity, and cooking confident

# Fast Food Model Variable elimination

## Test Colinearity

```{r}
# Linear model based on LASSO results
ff.linear.model <- lm(ff_numeric~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, data = bns_combined_imputed_df)

vif(ff.linear.model)



```

> There were no variables that were highly colinear in the fast food model

## Manual Backwards Elimination

```{r}

# Full Model Based on LASSO results

ff.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + kitchen_access + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()



```

### Test Removing Kitchen Access

```{r}

ff.ordinal.mod_KA <- with(bns_imputed_mids, MASS::polr(ff_cat~SNAP3 + Cohort + gender + race_eth + age + physical_activity + storage_room + health_conscious + living_with_family + cooking_confident + food_insecure_2item + paid_work_hours_tens + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()

tbl_merge(tbls = list(ff.ordinal.mod, ff.ordinal.mod_KA), tab_spanner = c("Full FF Model", "**Test Model*"))


```

> Kitchen Access had a high p value in the full model and can be removed without changing any results. No other covariates seemed like they can be removed. In the final fast food model, covariates will include cohort, gender, race/ethnicity, age, physical activity, storage room, health consciousness, living with family, cooking confidence, food insecurity, paid work hours, and homelessness in the past year.

# SSB Model Variable elimination

## Test Colinearity

```{r}
# Full model based on LASSO
ssb.linear.model <- lm(ssb_numeric~SNAP3 + Cohort + race_eth + gender + age + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + firstgen + household_size  + housing_insecure + homelessness_year, data = bns_combined_imputed_df)

vif(ssb.linear.model)

```

> There were no variables that were highly colinear.

## Manual Backwards Elimination

```{r}

ssb.ordinal.mod <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + firstgen + household_size  + housing_insecure + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


```

### Test Removing Household Size

```{r}

ssb.ordinal.mod.hz <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + food_insecure_2item + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + firstgen  + housing_insecure + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod, ssb.ordinal.mod.hz), tab_spanner = c("Full SSB Model", "**Test Model*"))

```

> Household size had a high p value in the full model and can be removed without changing any results

### Test Removing Food Insecurity

```{r}

ssb.ordinal.mod.fi <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + firstgen  + housing_insecure + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod.hz, ssb.ordinal.mod.fi), tab_spanner = c("Full SSB Model", "**Test Model*"))

```

> Food insecurity had a high p value in the full model and can be removed without changing any results

### Test Removing Firstgen

```{r}

# Remove firstgen
ssb.ordinal.mod.firstgen <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + housing_insecure + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod.fi, ssb.ordinal.mod.firstgen), tab_spanner = c("Full SSB Model", "**Test Model*"))


```

> Firstgen had a high p value in the full model and can be removed without changing any results

### Test Removing Housing Insecure

```{r}

ssb.ordinal.mod.HI <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + storage_room  + physical_activity + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod.firstgen, ssb.ordinal.mod.HI), tab_spanner = c("Full SSB Model", "**Test Model*"))



```

> Housing insecure had a high p value in the full model and can be removed without changing any results

### Test Removing Storage Room

```{r}

ssb.ordinal.mod.storage <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + living_with_family + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod.HI, ssb.ordinal.mod.storage), tab_spanner = c("Full SSB Model", "**Test Model*"))


```

> Storage room had a high p value in the full model and can be removed without changing any results

### Test Removing Living With Family

```{r}

ssb.ordinal.mod.LWF <- with(bns_imputed_mids, MASS::polr(ssb_cat~SNAP3 + Cohort + race_eth + gender + age + units_four + unpaid_work_hours_tens + paid_work_hours_tens + caregiving_hours_tens + health_conscious + storage_access + physical_activity + homelessness_year, Hess=TRUE)) %>% tbl_regression(exponentiate = TRUE) %>% bold_p()


tbl_merge(tbls = list(ssb.ordinal.mod.storage, ssb.ordinal.mod.LWF), tab_spanner = c("Full SSB Model", "**Test Model*"))

```

> Living with family had a high p value in the full model and can be removed without changing any results. No other covariates seemed like they can be removed. In the final SSB model, covariates will include cohort, gender, race/ethnicity, age, units, unpaid work hours, paid work hours, caregiving hours, health consciousness, storage access, physical activity, and homelessness in the past year.

# F&V Model Variable Elimination

## Test Colinearity

```{r}
# Linear model based on results from LASSO regression
fv.linear.model <- lm(q77_numeric~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, data = bns_combined_imputed_df)

vif(fv.linear.model)


```

> There were no highly colinear variables present

## Manual Backwards Elimination

```{r}

fv.ordinal.mod <- with(bns_imputed_mids, MASS::polr(fruits3~SNAP3 + Cohort + gender + race_eth + age  + health_conscious + cooking_confident + physical_activity + storage_room + food_insecure_2item + firstgen, Hess=TRUE)) %>% 
  tbl_regression(exponentiate = TRUE) %>% bold_p()


fv.ordinal.mod 

```

> No variables in the F&V model seemed like they can be removed In the final F&V model, covariates will include cohort, gender, race/ethnicity, age, health consciousness, cooking confidence, physical activity, storage room, food insecurity, and firstgenarational status.
:::
